### 2018-08-23 doc/latex/02-Software.tex
Add background information for gengeopop + template for other sections that have to be added to the manual
Add gengeo to manual

The project directory structure is very systematic.
Everything used to build the software is stored in the root directory:
\begin{compactitem}
    \item \texttt{main}: Code related files (sources, third party libraries and headers, ...)
      	\begin{itemize}
        		\item \texttt{main/<language>}: source code, per coding language: cpp (for C++), python, R,   
        		\item \texttt{main/resources}: third party resources included in the project: 
        \end{itemize}
    \item \texttt{doc}: documentation files (API, manual, ...)
      	\begin{itemize}
        		\item \texttt{doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
        		\item \texttt{doc/latex\_man}: files needed to generate the user manual with Latex
        \end{itemize}
    \item \texttt{test}: test related files (scripts, regression files, ...)
\end{compactitem}

@@

>>>>

The project directory structure is very systematic.
Everything used to build the software is stored in the root directory:
\begin{compactitem}
    \item \texttt{main}: Code related files (sources, third party libraries and headers, ...)
      	\begin{itemize}
        		\item \texttt{main/<language>}: source code, per coding language: cpp (for C++), python, R,
        		\item \texttt{main/resources}: third party resources included in the project:
        \end{itemize}
    \item \texttt{doc}: documentation files (API, manual, ...)
      	\begin{itemize}
        		\item \texttt{doc/doxygen}: files needed to generate the reference documentation with Doxygen
        		\item \texttt{doc/latex}: files needed to generate the user manual with Latex
        \end{itemize}
    \item \texttt{test}: test related files (scripts, regression files, ...)
\end{compactitem}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Protobuf
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Protocol Buffers}
\label{section:protobuf}
TODO

### 2018-08-23 doc/latex/03-Simulator.tex
Add gengeo to manual

\begin{compactitem}
    \item Binaries
    		in directory \texttt{<project\_dir>/bin}
      	\begin{itemize}
        		\item $stride$: executable.
        		\item $gtester$: regression tests for the sequential code.
                \item $gengeopop$: generates the population and geographical grid.
                \item $guilauncher$: tool to edit a simulation configuration and execute it
                \item $mapviewer$: tool to visualize the population and geographical grid, can be directly used from $stride$ and $guilauncher$.
                \item $calibration$: tool to run the simulator multiple times to generate statistical data. This can be used to calibrate test outcomes.
        		\item $wrapper\_sim.py$: Python simulation wrapper
        \end{itemize}
    \item Configuration files (xml and json)
      	in directory \texttt{<project\_dir>/config}
      	\begin{itemize}
		\item $run\_default.xml$: default configuration file for Stride to perform a Nassau simulation.
        \item $run\_generate\_default.xml$: default configuration file for Stride to first generate a population and geographical grid and then perform a Nassau Simulation.
        \item $run\_import\_default.xml$: default configuration file for Stride to first import a population and geographical grid and then perform a Nassau Simulation.
        \item $run\_regions\_default.xml$: default configuration file for Stride to first generate several regions with their own population and geographical grid and then perform a Nassau Simulation.
        \item $run\_regions\_import.xml$: default configuration file for Stride to first import several regions with their own population and geographical grid and then perform a Nassau Simulation.
        \item $run\_miami\_weekend.xml$: configuration file for Stride to perform Miami simulations with uniform social contact rates in the community clusters.
		\item $wrapper\_miami.json$: default configuration file for the wrapper\_sim binary to perform Miami simulations with different attack rates.
        \item \ldots
        \end{itemize}
    \item Data files (csv)
      	in directory \texttt{<project\_dir>/data}
      	\begin{itemize}
        \item $belgium\_commuting$: Belgian commuting data for the active populations. The fraction of residents from ``city\_depart'' that are employed in ``city\_arrival''. Details are provided for all cities and for 13 major cities.
		\item $belgium\_population$: Relative Belgian population per city. Details are provided for all cities and for 13 major cities.
		\item $contact\_matrix\_average$: Social contact rates, given the cluster type. Community clusters have average (week/weekend) rates.
		\item $contact\_matrix\_week$: Social contact rates, given the cluster type. Community clusters have week rates.
		\item $contact\_matrix\_week$: Social contact rates, given the cluster type. Primary Community cluster has weekend rates, Secondary Community has week rates.
		\item $disease\_xxx$: Disease characteristics (incubation and infectious period) for xxx.
		\item $holidays\_xxx$: Holiday characteristics for xxx.
		\item $pop\_xxx$: Synthetic population data extracted from the 2010 U.S. Synthetic Population Database (Version 1) from RTI International for xxx \cite{wheaton2014a,wheaton2014b}.
		\item $ref\_2011$: Reference data from EUROSTAT on the Belgian population of 2011. Population ages and household sizes.
		\item $ref\_fl2010\_xxx$: Reference data on social contacts for Belgium, 2011.

>>>>

\begin{compactitem}
    \item Binaries
    		in directory \texttt{<project\_dir>/bin}
      	\begin{itemize}
        		\item $stride$: executable.
        		\item $gtester$: regression tests for the sequential code.
                \item $gengeopop$: generates the population and geographical grid.
                \item $guilauncher$: tool to edit a simulation configuration and execute it
                \item $mapviewer$: tool to visualize the population and geographical grid, can be directly used from $stride$ and $guilauncher$.
                \item $calibration$: tool to run the simulator multiple times to generate statistical data. This can be used to calibrate test outcomes.
        		\item $wrapper\_sim.py$: Python simulation wrapper
        \end{itemize}
    \item Configuration files (xml and json)
      	in directory \texttt{<project\_dir>/config}
      	\begin{itemize}
		\item $run\_default.xml$: default configuration file for Stride to perform a Nassau simulation.
        \item $run\_generate\_default.xml$: default configuration file for Stride to first generate a population and geographical grid and then perform a Nassau Simulation.
        \item $run\_import\_default.xml$: default configuration file for Stride to first import a population and geographical grid and then perform a Nassau Simulation.
        \item $run\_regions\_default.xml$: default configuration file for Stride to first generate several regions with their own population and geographical grid and then perform a Nassau Simulation.
        \item $run\_regions\_import.xml$: default configuration file for Stride to first import several regions with their own population and geographical grid and then perform a Nassau Simulation.
        \item $run\_miami\_weekend.xml$: configuration file for Stride to perform Miami simulations with uniform social contact rates in the community clusters.
		\item $wrapper\_miami.json$: default configuration file for the wrapper\_sim binary to perform Miami simulations with different attack rates.
        \item \ldots
        \end{itemize}
    \item Data files (csv)
      	in directory \texttt{<project\_dir>/data}
      	\begin{itemize}
        \item $belgium\_commuting$: Belgian commuting data for the active populations. The fraction of residents from ``city\_depart'' that are employed in ``city\_arrival''. Details are provided for all cities and for 13 major cities.
		\item $belgium\_population$: Relative Belgian population per city. Details are provided for all cities and for 13 major cities.
        \item $flanders\_cities$: Cities and municipalities in Flanders with coordinates and population figures based on samples. These relative population figures are used for assigning residencies and domiciles based on a discrete probability distribution.
        \item $flanders\_commuting$: Relative commuting information between cities and communities. Since this data is relative, the total number of commuters is a derived parameter, based on the fraction of the total population that is commuting.
		\item $contact\_matrix\_average$: Social contact rates, given the cluster type. Community clusters have average (week/weekend) rates.
		\item $contact\_matrix\_week$: Social contact rates, given the cluster type. Community clusters have week rates.
		\item $contact\_matrix\_week$: Social contact rates, given the cluster type. Primary Community cluster has weekend rates, Secondary Community has week rates.
		\item $disease\_xxx$: Disease characteristics (incubation and infectious period) for xxx.
		\item $holidays\_xxx$: Holiday characteristics for xxx.
		\item $pop\_xxx$: Synthetic population data extracted from the 2010 U.S. Synthetic Population Database (Version 1) from RTI International for xxx \cite{wheaton2014a,wheaton2014b}.
		\item $ref\_2011$: Reference data from EUROSTAT on the Belgian population of 2011. Population ages and household sizes.
		\item $ref\_fl2010\_xxx$: Reference data on social contacts for Belgium, 2011.

### 2018-08-23 doc/latex/04-Code.tex
Add gengeo to manual

\subsection{Generating the geography}
\label{subsection:gengeo}
TODO

>>>>

\subsection{Generating the geography}
\label{subsection:gengeo}
We start by generating the geographical component, we call this a GeoGrid.
This contains locations with an id, name, province, coordinates and nominative population figures.
These locations contain multiple ContactCenters, like Schools and Households, which in turn contain ContactPools.
This structure is internally generated by several ``Generators" and will afterwards be used by ``Populators" to fill the ContactPools.
We construct the following types of ContactCenter:

\begin{description}
    \item[K-12 Schools]:
        These schools contain on average 500 students, with an average of 20 students per class, which corresponds to 25 ContactPools.
        The total amount of schools in the region is determined by the size of the population and the fraction of those people who attend a K-12 school.
        These generated schools are then assigned to a location by a draw from a discrete distribution based on the relative population size in each location.
    \item[Colleges]:
        These contain an average of 3000 students and 150 students per ContactPool.
        They are exclusively assigned to the 10 biggest locations in terms of population size.
        Within those 10 locations we again use a discrete distribution based on the relative population of the city compared to the total population in these top 10 cities.
    \item[Workplaces]:
        The assignment of workplaces is analogous to that of K-12 schools, but now we account for commuting information to determine the actual number of workers in a location.
        We find this amount by the working people who live there plus the people that commute to this location minus the ones that live there but commute away.
        A workplace contains on average 20 people.
    \item[Communities]:
        We create both primary and secondary communities, each containing 2000 persons from all ages and occupations.
        The assignement is analogous to that of K-12 schools.
    \item[Households]:
        The number of households is determined by the average size of a household in the reference profile and the total population size.
        The assignement is again analogous to that of K-12 schools.
\end{description}
